### 2022-06-06 README.Rmd
Added getssqparts to assist conditioning the MSE. No EWN
The option of hyperstability now correctly implemented, as is the expression of exploitable biomass through the year. No EWN.

>>>>

* 2022-06-06 aMSE 0.0.5. Have reviewed the dynamics in detail so that the outputs from the aMSE for each SAU more closely match the outputs from sizemod. The original disjunction was partly due to a faulty implementation of the inclusion of the option of hyper-stability, but that has now been amended and the operatnig model is now behaving as it should. Breaking the dynamics within each SAU into multiple sub-populations with variation also affects the equivalence between aMSE and sizemod butmostly influences the productivity rather than the recruitment dynamics and the trajectories mainly follow those from sizemod but with the cpue and biomasses being projected incorrectly. It appears (still working on a why) that by changing the productivity and sub-dividing that productivity among sub-populations, the overall recruitment levels required to mimic the dynamics in all cases appears to be less in aMSE than in sizemod. Otheriwse nothing now needs to change. One uses parameters obtained from sizemod, especially the recruitment deviates, and then apply the functions that search for more optimal values for AvRec, the unfished recruitment levles in each SAU. The fits obtained should be close to those found in sizemod. In 0.0.5 there remain issues relating to the internal data sets, which include one called 'zone', which is not designed to work with the option of hyper-stability (lambda != 1.0). Otherwise, No EWN.

* 2022-05-31 aMSE 0.0.4 Added functions that assist in conditioning the operating model by optimizing the fit to CPUE and size-composition data after opimizing the AvRec values for each SAU. No EWN.
